Determining the alternatives for scalar implicature

### 2016-01-31 Paper/Paper.Rmd
added condition descriptors to Exp 3 description. Changed topic sentence in Exp 3 results

Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation $(1)$. As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets. In the two-alternatives condition, participants made judgments for items included in the entailment scales. In the four-alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2. Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two-alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants. In the four alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.

@@

To test our secondary hypothesis, that the different sets of scalar items in the two conditions might result in differences in pragmatic judgments for the same items, we fit a mixed effects model. We regressed pragmatic judgments on scale and condition with subject- and word-level random effects, which was the maximal structure that converged. There were no significant differences between conditions, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.

@@

Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model. Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed. We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.

@@

While improvements in model fit were substantial as we moved from two to four alternatives, we saw only a minor increase in fit from the move to five alternatives. One possible explanation is that alternatives are differentially salient in context, and moving to larger sets would consider weighting the alternatives differentially [as @franke2014 did]. Preliminary simulations using weightings derived from Experiment 2 provide some support for this idea but would require further empirical work for confirmation.

>>>>

Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation $(1)$. As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets. In the two-alternatives condition (Experiment 3a), participants made judgments for items included in the entailment scales. In the four-alternatives condition (Experiment 3b), participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2. Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

We recruited 100 participants from AMT, 50 for each condition. Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants. In the four alternatives condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.

@@

To rule out the potential effects of having a larger set of alternatives  during  the  pragmatic  judgment  elicitation, we fit a mixed effects model. We regressed pragmatic judgments on scale and experimental condition with subject- and word-level random effects, which was the maximal structure that converged. There were no significant differences between conditions 3a and 3b, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.

@@

Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model. Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed. We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative \footnote{literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline "none" style semantics in which the scalar item is only compatible with 1 star}, 3) the expanded set of four alternatives tested in Experiment 1b, and 4) the expanded set of five alternatives tested in Experiment 1c.

@@

While improvements in model fit were substantial as we moved from two to four alternatives, we saw only a minor increase in fit from the move to five alternatives. One possible explanation is that alternatives are differentially salient in context, and in moving to larger sets we should consider weighting the alternatives differentially [as @franke2014 did]. Preliminary simulations using weightings derived from Experiment 2 provide some support for this idea but would require further empirical work for confirmation.
